\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex
paper: fcc -> freeCodeCamp

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp (fCC) as a part of a survey of new software developers
(both professional and amateur)~\cite{fcc-data}. freeCodeCamp is an open-source
community that helps users learn how to program. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
demographic and programming-related questions.
The survey targeted users who were related to coding organizations.

@@

Our second set of queries is on the fCC data (\Cref{fig:queries-fcc}).
\Cref{q5} calculates the average income for survey participants, based on their bootcamp attendance.
\Cref{q6} estimates the average commute time of women from the United States who participated.
\Cref{q7} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q8} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita of countries with and without bootcamp participants.

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on fCC data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}

>>>>

\subsubsection{freeCodeCamp 2016 New Coder Survey}
For our second set of experiments, we chose to use data collected
by freeCodeCamp as a part of a survey of new software developers
(both professional and amateur)~\cite{fcc-data}. freeCodeCamp is an open-source
community that helps users learn how to program. Their \textit{2016 New Coder Survey} consists of responses by over 15,000 people to 48 different
demographic and programming-related questions.
The survey targeted users who were related to coding organizations.

@@

Our second set of queries is on the freeCodeCamp data (\Cref{fig:queries-fcc}).
\Cref{q5} calculates the average income for survey participants, based on their bootcamp attendance.
\Cref{q6} estimates the average commute time of women from the United States who participated.
\Cref{q7} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q8} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita of countries with and without bootcamp participants.

\begin{table*}
  \centering
  \begin{subtable}{\linewidth}
    \input{queries-cdc}
    \caption{Queries on CDC data}\label{fig:queries-cdc}
  \end{subtable}
  \par\medskip
  \begin{subtable}{\linewidth}
    \input{queries-fcc}
    \caption{Queries on freeCodeCamp data}\label{fig:queries-fcc}
  \end{subtable}
  \par\medskip
  \caption{Queries used in our experiments.}\label{fig:queries}
\end{table*}
